Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-27 paper/structureScene.tex
finish writing subsection IV. C

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design, and their distribution is typically skewed towards the right.

This issue can be addressed by applying to all coefficients a pointwise concave transformation, \eg logarithmic, hence reducing skewness.
In particular, logarithmic compression is ubiquitous in audio signal processing, as it is corroborated by the Weber-Fechner law in psychoacoustics, which states that the sensation of loudness is roughly proportional to the logarithm of the acoustic pressure.
In the context of auditory scenes, we must also stress that the measured amplitude of sound sources often decays polynomially with the distance to the binaural microphone.
Logarithmic compression can linearize this dependency, which arguably facilitates the construction of an invariant to this distance at the classifier stage.

And\'en \cite{Anden2014}
\begin{equation}
\log \dfrac{\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2)}{\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)} =
\log \mathbf{S_2}\boldsymbol{x}(t, \gamma_1, \gamma_2) -
\log \mathbf{S_1}\boldsymbol{x}(t, \gamma_1)
\end{equation}

>>>>

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design, and their distribution is typically skewed towards the right.
This issue can however be addressed by applying to all coefficients a pointwise concave transformation, \eg logarithmic, hence reducing skewness.

In particular, logarithmic compression is ubiquitous in audio signal processing, as it is corroborated by the Weber-Fechner law in psychoacoustics, which states that the sensation of loudness is roughly proportional to the logarithm of the acoustic pressure.
In the context of auditory scenes, we must also recall that the measured amplitude of sound sources often decays polynomially with the distance to the binaural microphone, which is a spurious factor a variability to the task of auditory scene classification.
Logarithmic compression can linearize this dependency, which arguably facilitates the construction of a powerful invariant at the classifier stage.

Given a task of musical genre recognition, \cite{Anden2014} has advocated for the renormalization of second-order scattering coefficients $\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2)$ by the corresponding first-order scattering coefficients $\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)$, as it provably decorrelates the amplitudes of their activations.
Interestingly, taking the logarithm of renormalized coefficients would yield
\begin{equation}
\log \dfrac{\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2)}{\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)} =
\log \mathbf{S_2}\boldsymbol{x}(t, \gamma_1, \gamma_2) -
\log \mathbf{S_1}\boldsymbol{x}(t, \gamma_1),
\end{equation}
\ie a linear combination of the logarithms of first- and second-order coefficients.
Therefore, the theoretical insight brought by \cite{Anden2014} in favor of renormalized scattering also applies to log-scattering up to a linear transformation in feature space, to which affine classifiers are not sensitive.
